---
title: "The Transform 2030 data-set"
author:
  name: Oscar Widerberg, Cornelia Fast, Montserrat Koloffon, Philipp Pattberg
  email: oscar.widerberg@vu.nl
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 3
    number_sections: yes
    smooth_scroll: yes
    fig_caption: yes
    theme: paper
institute: Institute for Environmental Studies (IVM), Vrije Universiteit Amsterdam
abstract: "The Sustainable Development Goals (SDGs) have been criticized for compartmentalizing issue areas and neglecting the interconnections between global challenges such as climate change, biodiversity loss and poverty reduction. Multi-stakeholder partnerships (MSPs) - including public, private and civil society organizations - play an important role in implementing the 2030 Agenda (see SDG 17) and might offer a vehicle for creating synergies between issue areas and thus bring about transformative change. This technical report maps and analyzes existing and recently concluded MSPs with the  potential to address multiple SDGs simultaneously. It provides a detailed description of the background, methodology, and key observations from building a database of MSPs that work on two or more SDGs, serving as an empirical basis for the multi-year project Transformative partnerships for sustainable development: Assessing synergies, effectiveness, and legitimacy of the UN’s multi-stakeholder partnerships across SDGs to achieve the 2030 Agenda"
bibliography: references.bib
---

```{r, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE}
  
  source("01_Libraries and custom functions_v1.R")

```

```{r, echo=FALSE, warning=FALSE, warning=FALSE, message=FALSE}

source("02_Read in data and create R objects_v1.R")

```

<br>

***Key messages***

-   MSPs have the potential to connect the environmental SDGs (climate change, water and biodiversity) in particular, with social and economic targets (notably energy, education, health and hunger).

-   Clean water and changing consumption and production patterns are the least connected SDGs through MSPs.

-   About 56 % of MSPs show online activity, 22 % have been concluded and 22 % have no sign of online activity.

-   Large UN summits (e.g. Rio +20, UNFCCC COP21, and the Ocean Conferences) are popular venues for launching new MSPs or rebranding existing ones

-   Public authorities, in particular international organizations and national governments, are most prevalent members in MSPs

-   Nearly half of MSPs have 'knowledge dissemination' as key function. The least popular function is finance and service provision.

# Introduction

Multi-stakeholder partnerships between public, private and civil society organizations are expected to play an integral role in implementing the Sustainable Development Goals (SDGs) and the 2030 Agenda. In 2015, when the United Nations General Assembly's adopted the 2030 Agenda and the SDGs, UN member states emphasized the role of multi-stakeholder partnerships (MSPs) through Goal 17 - '*Strengthen the means of implementation and revitalize the Global Partnership for Sustainable Development' @un2015*. MSPs are expected to address challenges across geographies and to "mobilize and share knowledge, expertise, technology and financial resources" to support the implementation of Agenda 2030 [@un2015, pp.27]. Subsequently, the need to accelerate and scale up action was pronounced both through the launch of the Decade of Action in 2020 and at the Stockholm+50 conference in 2022. A key feature to accelerated action is to understand and address the interconnected nature of global challenges such as climate change, biodiversity loss and poverty reduction. Climate change, for instance, is changing precipitation patterns which in turn puts pressure on ecosystems and local communities' ability to sustain themselves and thereby undermine poverty alleviation efforts. Consequently, addressing environmental, social and economic SDGs together could generate greater benefits than focusing only on single targets. MSPs may be considered vehicles for creating synergies between two or more SDGs.

## Why multi-stakeholder partnerships

MSPs set up to address global sustainability challenges proliferated substantially in the early 2000's. Mega-conferences on sustainable development and environmental issues have proven to be fertile grounds for new MSPs to arise or old ones to reinvent themselves. During events such the World Summit on Sustainable Development in 2002 and the Rio+20 Conference on Sustainable Development in 2012, as well as, conferences in adjacent issue areas such as the COP21 to the United Nations Framework Convention on Climate Change (UNFCCC) in 2015, a relatively high number of new MSPs have been observed. Proponents of MSPs laud the rise of partnerships, emphasizing their potential to provide effective governance where governments and international organizations are incapable of acting on their own [@liese2011]. Public, private and civil society organizations could share resources and expertise to implement global development goals through networks, making the whole greater than the sum of the parts. Inter-sectoral cooperation could also increase legitimacy of global governance by engaging actors from various parts of society, including vulnerable and under-represented groups. However, critics of MSPs, however, focus instead on the risks of outsourcing implementation to an indistinct and heterogeneous group of actors, enabling governments to shirk commitments made in inter-governmental fora, and masking and entrenching existing power-asymmetries - mainly favoring corporate business and NGO elites, with the UN's and the SDG's seal of approval, sometimes referred to as "blue-washing" [see e.g. @bäckstrand2008; @zammit2003]. Existing research on MSPs launched over the past 20-years appears to fuel the critics' fires. Beyond single cases of highly influential and visible MSPs such as Gavi, the Vaccine Alliance or the Renewable Energy and Energy Efficiency Partnership (REEEP), there is little systemic evidence supporting the narrative that MSPs are effective, legitimate and transformative. For instance, a review of 340 partnerships in 2012, found that over 60 % were inactive, lacked observable output or did not operate in line with their own ambitions [@pattberg2012]. A more recent effort by Andonova and colleagues, explores a small but rich data-set of MSPs for sustainability and concludes that neither the proponents nor the critics can be declared winners [-@andonova2022]. They point towards a 'partnership paradox' which holds that partnerships make large promises without clarifying what they exactly deliver and call for more research, including new data and methodologies for studying various pathways to effectiveness [@andonova2022, p.275].

## Why the Transform 2030 data-set

Following in the footsteps of Andonova and colleagues, and heeding the call for more data and new methods, this report presents the Transform 2030 data-set. The data-set focuses on transnational MSPs that aim to connect two or more SDGs. It consists of a subset of entries on the Partnership Platform maintained by United Nations Division of Economic and Social Affairs (UN DESA) which functions as a global registry of voluntary commitments and partnerships to achieve the SDGs. The platform currently hosts an impressive number of nearly 7,000 entries created by stakeholders that voluntarily register their initiatives [@undesa2022]. The entries differ widely in type, size and ambition, however. Some are multi-million dollar endeavors with secretariats of permanent staff and resourceful partners spread across the globe. Others are actions taken by single individuals, companies, and local communities with limited resources or reach. Strictly speaking, few can be called transnational multi-stakeholder partnerships. In this report, we aim to stay close to the definition and operationalization of MSPs for sustainability used by global governance researchers including *inter alia* Andonova and colleagues [-@andonova2022], Bäckstrand [-@bäckstrand2006], Beisheim and Liese [-@beisheim2014], and Pattberg and colleagues [-@pattberg2012] (see Annex 1 for methodological notes). However, we used a tiered approach to determining whether the MSPs fall within a narrow or broad definition. The report is an output of the research project 'Transformative partnerships for sustainable development: Assessing synergies, effectiveness, and legitimacy of the UN's multi-stakeholder partnerships across SDGs to achieve the 2030 Agenda', funded by Formas, the Swedish Research Council for Sustainable Development, the project comprises international relations and political science scholars from Stockholm University, Lund University and the Institute for Environmental Studies, Vrije Universiteit Amsterdam. The aim of the research project is to explain the extent to which MSPs are potential tools for effective, synergistic, and inclusive governance. Furthermore, it assesses under what conditions UN partnerships for sustainable development can contribute to achieve the 2030 Agenda and accelerate transformative shifts toward sustainability.

## Aim of this report

In this report, we aim to do two things. First, describe the characteristics of the MSPs' in the data-set, including their partner composition, functions and the specific SDGs they connect, and second, to illustrate to what extent MSPs simultaneously address multiple SDGs. As a result of the mapping exercise, this report highlights key trends among a set of global MSPs and raises questions about its implications for their role in governing synergies between SDGs. Consequently, it provides entry points for future research about the effectiveness, legitimacy and accountability of MSPs within and beyond the Transform 2030 research project. Moreover, the report outlines a novel methodology for doing research on MSPs and is explained in detail in annex 1 and 2. The outline of this technical report is as follows. In section 2 we presents the descriptive statistics of the data-set. In section 3, we describe the potential synergies. And in section 4, we draw conclusions from our findings, list key messages and provide suggestions for future research avenues.

# Methods and materials

In this section, we briefly explain the methodological choices and steps taken to assemble the Transform 2030 data-set. For technical information, please visit the annexes to this report.

The methodology for compiling the Transform 2030 data-set consists of both automated methods (using computer-based techniques) and manual coding. It builds on, but also extends, the logic and proven methods, operationalizations and coding for gathering similar data-sets, for instance, the CONNECT-data on international cooperative initiatives for climate change [@widerberg2016], forests [@diasguerra2015], and, fisheries [@arnau2017]; the CLIMENGO-data on initiatives in the climate-energy nexus [@sanderink2018]; and, the Bio\* data on biodiversity initiatives [@negacz2020]. The following four steps were taken to assemble the data-set.

First, we use the [Partnership Platform](https://sdgs.un.org/partnerships) as a source to find MSPs that fit the Transform 2030 project goals. The platform is maintained by United Nations Division of Economic and Social Affairs (DESA) and contain some 7,000 entries made by, what DESA refers to as, "stakeholders". All available information on the entries were downloaded from the website by building and running a web scraper in R. The scraping, carried out on February 2nd 2022, rendered 6936 entries. Duplicates were removed computationally by name of the entry, excluding `r 6936-nrow(committments)` entries, leaving `r nrow(committments)` for further analysis.

Second, the Transform 2030 project is interested in MSPs working across SDGs. Each entry on the Partnership Platform contains information regarding to which SDGs the stakeholders themselves believe they contribute. However, such information is highly dependent on each stakeholder's understanding and knowledge of the SDGs. To control for such biases in the data, we instead choose for a dictionary-based approach to identify which SDGs the entries target. It entails developing a dictionary of keywords for each SDG and their targets using the '[Global indicator framework for the Sustainable Development Goals and targets of the 2030 Agenda for Sustainable Development](https://unstats.un.org/sdgs/indicators/Global%20Indicator%20Framework%20after%202020%20review_Eng.pdf)'. For instance, SDG 1. *End poverty in all its forms everywhere.* would be associated for words such as "poverty", "land tenure", and "social protection". In total, `r nrow(dictionary)` keywords and phrases were identified (see Annex 2 for a complete list). The dictionary was applied using automated content analysis to the descriptions of the `r nrow(committments)` entries from step 1, and those only addressing one SDG were excluded for further analysis. Also entries that didn't provide a website were excluded, leaving 2452 entries for further analysis.

Third, since stakeholders are free to upload whatever they see fit, the Partnership Platform comprises a hotchpotch of initiatives, commitments, programs, projects, plans and partnerships. Only a few of these can be labelled MSPs. To determine which entries that could qualify as an MSP, the team developed a protocol consisting of four questions by operationalizing Andonova's definition of MSPs which reads "*Voluntary agreement between public and non-state actors on a set of governance objectives and norms, rules, practices, implementation procedures, across multiple jurisdictions and levels of governance*" [@andonova2017]. The protocol consists of four criteria: (1) if the entry involves different public, private or civil society organizations; (2) if the partners were based in more than one country; (3) if the entry was targeting more than one jurisdiction; (4) if the entry has a high or low level of institutionalization (tier 1 or 2), that were applied manually to the 2452 entries. Only entries with a positive answer to the four questions, were considered eligible for next steps, leaving around `r nrow(MSPs)` entries for further analysis.

> *The MSPs in the data-set are sub-divided into two tiers according to whether they adhere to a strict or a loose definition of MSPs. The first group ("Tier 1") apply a narrow definition of MSPs. The second group ("Tier 2") apply a more loose definition. In the description of the findings, we present both tiers separately.*

Four, the entries were coded across 48 variables, including basic information, partners, and function. Data from the PRIO data-set were merged with the entries, and further refined based on a 24-page code-book (further developing, expanding and refining the PRIO project's code-book). The code-book also contains detailed information for the coding of in step 3 (access the code-book [here](https://stockholmuniversity.box.com/s/23mz6fg0q9e3warpn4yydpp9fh3v88kk)). The results of the coding are presented in the following sections.

For more detailed information on specific parts of the methodology, including caveats and remedies, please see the annexes.

# Findings

This section describes the findings of the assembly of the Transform 2030 data-set. It starts with an analysis of level of activity, second, it describes which SDGs that are most and less frequently connected in the MSPs revealing potential synergies. Subsequently, a number of descriptive statistics are presented, including start and end-years, type of partners, countries more mentioned, and functions. Finally, the conclusions summarizes the main findings from mapping various characteristics and look ahead towards future research.

## Activity level

The Partnership Platform encourages but does not require stakeholders that put entries on their platform to provide evidence of any activity or impact. In previous iterations of the Platform, stakeholders were able to upload progress reports, that feature is currently disabled. Few stakeholders, however, seem to have made use of the opportunity to upload progress reports. A pilot study to the Transform 2030 project looked at some 1,600 entries on the Platform and found that a mere 15 % had provided a progress report [@koliev2022]. The findings resonate with earlier research on MSPs which suggests that many partnerships disintegrate after their launch. A 2012 review of 340 partnerships launched during the World Summit on Sustainable Development in 2002, showed that nearly 40 % didn't show any activity whatsoever five years after their presentation in Johannesburg [@pattberg2012]. In the Transform 2030 data-set, the numbers are not quite that bad. Out of `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(1,2,3,4)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` MSPs, `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(3)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` are currently active, while an additional `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(4)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` showed signs of having been active online before the Covid pandemic hit in 2019. These make up in total `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(3,4)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` observations that are active and/or have been concluded. Some `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(1)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` MSPs, equal to 13 % of the sample, show no online activity beyond their entry on the Partnership Platform, another `r committments %>% filter(addresses_more_than_one_sdg.x == 1, signs_of_life %in% c(2)) %>% filter(level_of_institutionalisation %in% c(1,2,3)) %>% nrow()` MSPs, equal to 8 %, have some sign of activity online, e.g. launch, but nothing beyond that, meaning that some 22 % of the MSPs never seem to have been active online in any meaningful sense.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 1. Level of activity in MSPs"}

source("06_Activity level_v1.R")
ggplotly(signs_of_life_figure)

```

Since we are mainly interested in currently or recently active, as well as, concluded MSPs, the following sections focus on the sample of 371 MSPs.

## Start and end years

Environmental mega-conferences such as the WSSD, Rio+20, the UNFCCC COPs 15 and 21, as well as, the Ocean Conferences, have become popular venues for launching or re-branding MSPs. UNDESA itself is seemingly aware of this, arguing that the Partnership Platform "brings together different registries launched in support of various UN conferences and processes dealing with sustainable development over the years" [@undesa2022]. The Transform 2030 database confirms this picture suggesting that the Rio+20 conference in 2012, UNFCCC COP21 in Paris in end 2015, the first UN Ocean Conference held in New York in 2017, functioned as important launchpads. Figure 2 plots the self-reported launch year of the MSPs, which makes it possible to study how the number of MSPs have evolved over time.

```{r figure 2, echo=FALSE, warning=FALSE, fig.cap="Figure 2. MSP's starting year"}

source("06_Starting year figure_v1.R")
ggplotly(start_year_figure)

```

Figure 2 shows that 2014 is comparable to 2012 in terms of number of MSPs that were being launched. This could potentially be explained by the 2014 SIDS Conference taking place. In 2015, the 2030 Agenda was launched in summer followed by the Paris Agreement being signed in autumn at the COP21 Climate Conference. We observe relatively high numbers of starting dates in 2015, and even higher in the aftermath of these two international events on sustainability, in 2016. Finally, the largest number of MSPs were launched in 2017, which is likely explained by the UN Ocean Conference. One can also speculate why no MSPs were launched in some years. For instance, the low number in 2020 could be due to the start of the COVID19 pandemic, despite the fact that there were partnerships set up in response to the pandemic (e.g. the COVAX initiative, which is not featured on the Partnership Platform). The MSPs, launched before the adoption of the SDGs in 2015, initially were set-up to address the MDGs that were adopted in 2000. Finally, 90 MSPs have no information about their starting year, these been excluded from the Figure 2.

Figure 3 provides an overview of the end year as stated by the MSPs. The most popular end year is 2030 which makes sense in terms of congruence with the 2030 Agenda. However, the data also suggests that many MSPs on the platform should already have been concluded. The majority of MSPs have 2020, 2021, or 2022 as end year, suggesting that many of them consider themselves time-bound initiatives with decisions on continuance decided at a later stage. The data quality however is similar to starting year, with 57 MSPs providing no end-date and one providing 2099 as end-date.

```{r, echo=FALSE, warning=FALSE, fig.cap="Figure 3. MSPs’ end year"}

source("07_End year figure_v1.R")
ggplotly(end_year_figure)

```

The start and end year data could be interpreted in several ways. They demonstrate that mega-conferences fill an important function for MSPs as launchpads. It also suggest that the 2030 Agenda has become an anchoring point for many MSPs. The missing data on about 24 % of the MSPs could either be understood as purposeful actions of the stakeholder entering the data, with no plan for an end-year, or as an unintentional act, where the data was simply omitted due to time or knowledge constraints.

## Partners

MSPs in the past have often been launched, led, and maintained by international organizations and national government, sometimes in cooperation with large and resourceful NGOs [see e.g. @unep2018; @mert2015; @pattberg2012]. The Transform 2030 data-set follows a similar pattern. Figure 3 provides an overview of the distribution of partners.

```{r, echo=FALSE, warning=FALSE, fig.cap="Fig 4. Number of MSPs per type of partner"}

source("08_Partner figure_v1.R")
ggplotly(partner_figure)

```

International organizations (IOs) are the most common type of partner. In fact 67% (n=251) of all MSPs have at least one IO as a partner. These are of different sizes and have a varied geographical reach (e.g. global, regional). IO's are perhaps logical partners for transnational MSPs, meaning that they have partners from and also target more than one country. The second most common partner type are national governments and state actors, which include different bodies of the state apparatus such as ministries and government agencies. Together, the two most common types of partners give the indication that MSPs have at least one partner that are connected to state governance, such a state funding, while non-government organizations (including not-profit organizations) and the scientific community (e.g. universities and research institutes) are present in slightly fewer MSPs.

Private actors such as corporations and businesses are part of approximately half of the MSPs. The least common type of partners are local governments (e.g. regions, municipalities) and labor unions. Perhaps again the focus on transnational MSPs is to part of the explanation. While local governments do engage in global initiatives for the purpose of knowledge exchange and visibility, they also benefit from engaging in partnerships within their own national or regional jurisdiction. Moreover, labor unions tend to operate on a national scale within a certain legal framework rather than internationally. The mapping also showed that a handful have MSPs as partners. 

As a reminder, our data is limited to indicating which sectors that are represented in the MSPs, rather than describing the number of partners from each sector. This means, for example, that there could be, in total, more stakeholders from the scientific sector that act as partners in the MSPs than e.g. NGOs. In terms of total number of partners, however, the MSPs vary between being bilateral partnerships with two partners, to larger MSPs gathering over 700 partners. While most MSPs can be found evenly distributed along the range of 2-200 partners, a handful belong to the group of larger MSPs with 200-700 partners. By dividing the stakeholders that participate in MSPs into eight different types, we find that most MSPs are composed of partners from 2-4 different sectors, while only a few have as many as stakeholders from 6-8 different sectors working together. 

## Country

Studying which countries that mostly engage in MSPs could lead to important insights in terms of representation, inclusiveness and justice. MSPs have traditionally been led and dominated by countries in the Global North [see e.g. @mert2015]. While being an important issue, it is notoriously difficult to study. The Partnership Platform data quality is highly problematic when it comes to country representation and unfortunately, countries are not reported systematically by entries in the platform, and therefore could be pointing to different information including: Entries may report where their headquarters, Secretariat or offices are located; Entries may report the countries where their partners are located or active; Entries may report the countries that their work is targeting; The reported countries may be a mix of the above options. Considering these caveats, the distribution of countries provide useful indicators of where action is being taken. Figure 4 displays a list of countries that MSPs most often mention that they are connected to.

```{r, echo=FALSE, warning=FALSE, fig.cap="Figure 5. Countries with connections to MSPs in dataset (>8 threshold)"}

source("09_Country figure_v1.R")
ggplotly(country_figure)

```

The 25 most commonly mentioned countries reported by 8 MSPs or more. Notably, among the 10 most mentioned countries, we find representation of at least one country from every continent (Africa, North America, South America, Asia, Europe, and Oceania). These frequently mentioned countries, however, also appear to correlate with countries hosting UN organizations. Six out of the 10 most mentioned countries by Tier 1 MSPs host at least two headquarters of UN organizations (United States, Kenya, France, Switzerland, the Netherlands, and Germany).

Furthermore, while among this cutoff of most frequently mentioned countries we find most countries to be European, the 2nd most mentioned countries belong to Oceania, which shows the strong connection of this registry to certain conferences, such as the Ocean Conference. While the US takes the first place among the most frequently mentioned countries, in terms of regions, the lowest representation is of countries from the Americas, among which we only find the US, and Brazil.

## Functions

MSPs are generally been engaging in "soft" governance functions such as providing venues for networking, knowledge-exchange, and information gathering. Looking at figure 6 on functions in the Transform 2030 data-set suggest that the trend continues and that the most common function carried out by the MSPs is knowledge dissemination, meaning that they in some way distribute knowledge or share experiences horizontally or vertically to other stakeholders.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 6. Number of MSPs per type of function"}

source("10_Functions figure_v1.R")
ggplotly(function_figure)

```

Four functions - capacity building, participation management, technology transfer and training - share the spot for second most common functions. Moreover, the fact that these four functions had a similar placement along the scale can be explained by the fact that they are closely related. Capacity building often goes hand-in-hand with technology transfer and training activities.

Most MSPs (50%) perform three or four different functions, either simultaneously or at different stages throughout their lifetime. Furthermore, while not illustrated in the graph, the mapping also showed that 75% of MSPs report the type of resources they have at their disposal to carry out their functions and maintain their operations. This means that 25% either do not have resources such as staff, technical expertise or financing, or simply do not report on them. The results mirror previous findings in the global climate governance field, e.g. UNEP Emissions Gap Reports in 2018 where knowledge production and dissemination was the most common function [@unep2018]. Norm-setting and financing/funding functions are, like in our sample, less common. The results also support the recent findings from the PRIO data-set, where finance was the least common function whilst technology and knowledge transfer and training and capacity building was the most common.

## Synergies

A new under-explored field of study in MSP research is that of synergies, trade-offs and conflicts between various goals that they are trying to accomplish. Our analysis on SDGs connections and potential synergies suggest that the majority of MSPs keep it contained to two or three SDGs simultaneously, see figure 6. Thereafter, the distribution declines successively as the number of SDGs grows, with three and four SDGs being the second and third most common number of SDGs addressed by MSPs. Only a handful of MSPs address as many as seven, eight or nine SDGs at the same time.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 7. Number of MSPs per number of SDGs addressed"}

source("11_Number of SDGs figure_v1.R")
ggplotly(number_of_SDGs)

```

Plotting the SDGs in a heatmap makes it possible to identify the degree to which SDG dyads are connected through MSPs. The environmental targets are particularly popular to connect in MSPs. The most frequently featured dyad is SDG 13 (Climate Action) and SDG 15 (Life Below Water), which is included in 58 MSPs, followed by SDGs 14 and 15 (Life on Land), included in 50 MSPs. Finally, SDGs on the third spot of most connected pairs there's a tie between the pair of SDG 13 and 15, together with the pair of SDGs 3 (Good Health and Wellbeing) and 4 (Quality Education), both connected by 63 MSPs. This points to opportunities for potential synergies within the climate-biodiversity nexus, as well as within the health-education nexus, but the most connected pairs are not between the three sustainable development areas (environmental, social, economic). The least connected SDG overall, is SDG 12 (responsible consumption and production), which never appears in combination with 10 out of the other 16 SDGs, and is overall the least popular SDG in the focus of MSPs in the sample.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 8. Overview of SDG dyads addressed by MSPs"}
source("03_Keyword analysis_v1.R")
source("05_Network analysis_v1.R")
source("12_Heatmap figure_v1.R")
ggplotly(heatmap_figure)

```

While Figure 7 presents a gradient overview of how frequently SDG combinations are addressed by MSPs, we also performed a network analysis to zoom in on the most frequent combinations. This approach primarily consisted of projecting a bipartite network of MSPs and SDGs into two unipartite networks, connecting MSPs and SDGs. The network in Figure 8 presents how the 17 SDGs are connected.

```{r echo=FALSE, fig.height=7, fig.width=10, warning=FALSE, fig.cap="Figure 9. Network in circle layout (most frequent connections in pink)"}

source("13_Network figure_v1.R")
network_figure_circle

```

The pink lines in the network figure indicate that the pairs of SDGs that most MSPs address are Goal 13 (Climate Action), Goal 14 (Life Below Water) and Goal 15 (Life on Land) are connected most often. Out of the most commonly connected SDGs, Goal 13 (Climate Action) is connected to the largest variety of goals, followed by Goal 14 (Life Below Water) and Goal 3 (Health). In contrast, Goal 2 (hunger), Goal 5 (Gender Equality) and Goal 11 (Cities) only have strong connections to one other SDG each. In figure 9 the same data is shown but using an algorithm that cluster SDGs that are more tightly connected.

```{r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=6, "Figure 10. Clustering of SDGs in the network"}

network_figure_fm

```

The analysis clearly shows that the environmental goals (13,14 and 15) are forking a tight cluster in the network. In particular, SDG 13 on climate in particular is popular among the MSPs. Also the goals on energy, cities, health, and education are well connected and represented in among the MSPs. Economic goals, including 12 on consumption and production and 9 on innovation are the least connected to the other SDGs.

# Conclusion and Research Questions

This report provides an overview of the Transform 2030 data-set, including the methodology used for assembling and analyzing the data, as well as, a bird's-eye view of the findings. Assembling the final data-set has shown that the landscape of global efforts recorded in the Partnership Platform is highly heterogeneous.The relatively high number of active MSPs is a positive signal compared to previous research which found an even larger number of inactive MSPs emerging from the WSSD (see introduction). The final number of MSPs may seem small compared to the nearly 7,000 entries on the Partnership Platform, however, it is in the same order of magnitude of similar data-collection exercises in sustainable development, climate change and biodiversity. The finding raises question of why there appears to be an upper limit for how many transnational MSPs there are working on sustainability at any given moment of time.

Second, MSPs in the Transform 2030 data-set suggest that the environmental goals and targets, in particular SDG13 (Climate Action), SDG14 (Life Below Water) and SDG15 (Life on Land) are most often connected by MSPs, followed by SDG7 (energy) and SDG2 and 3 (Hunger and Health). SDGs 12 (consumption and production) and SDG9 (innovation) are much less connected to other SDGs via the MSPs. The findings demonstrate where the largest potential synergies could be found but also which SDGs that still may require more attention from MSPs. Future research should focus on understanding why certain SDGs appear to be more connected than others, and whether the connections are the ones with the most transformative potential.

Third, the descriptive statistics suggest that a typical partnership consists of partners from the Global North (in particular USA, France and the Netherlands) and an international organization. It was launched during one of the environmental mega-conferences and carry out soft governance functions such as knowledge sharing and dissemination. It connects two SDGs and is expected to have finishing date around 2030. Future research could aim to understand how institutional set-ups (e.g. partners, starting-year and function) of MSPs correlate with the SDGs that they combine. Are some type of MSPs more or less likely to address a combination of SDGs, and why is that the case? It also begs questions on longevity and stickiness. Why are some partnerships able to launch, attract partners and thrive during an extended period of time, whereas many seem to dissipate after launch or after a few years or operation?

Fourth, the Transform 2030 data-set only show where potential synergies between SDGs are most likely to happen. The next step would be to investigate actual synergies, trade-offs and conflicts between targets, as well as, whether MSPs are effective in exploring their potentials. Moreover, are MSPs able to be effective while also fulfilling their promises of enhancing legitimacy in global sustainability governance through, for instance, inclusiveness.

Finally, how can the UN or other bodies be conducive for the landscape of MSPs to be effective? It raises the question of meta-governance, whether it is necessary and if so, in what shape and form. For instance, what changes, if any, could be made to the Partnership Platform to enable MSPs and analysts to better understand what works and under what conditions the promises of MSPs can be fulfilled.

# References

::: {#refs}
:::

# Acknowledgements {.unnumbered}

This report, including the methodology for constructing the data-set, has benefited greatly from input from all the project members of the Transform 2030 project, including the Scientific Advisory Board (see: transform2030.se), in particular the early data-collection and conceptual work by Faradj Koliev, Essraa Hussein, and Ian Higham, carried out partly under the PRIO project, which analysed some 1,600 entries on UNDESA's Partnership Platform. The data-collection team at IVM has also received invaluable assistance from Julia van Heese. The project is funded by FORMAS, the Swedish Research Council for Sustainable Development, under the name *Transformative partnerships for sustainable development: Assessing synergies, effectiveness, and legitimacy of the UN's multi-stakeholder partnerships across SDGs to achieve the 2030 Agenda* (2020-00418).

# Annexes {.unnumbered}

## Annex 1 - Methodology {.unnumbered}

This methodological annex contains technical information on specific steps of the methodology, in addition to the description of the method in section 2.

### Web scraping {.unnumbered}

The web scrapes was built using R-packages rvest and tidyverse. The data set is built on information scraped from the homepage: <https://sdgs.un.org/partnerships/browse>, on 2nd February 2022.

### Text analysis {.unnumbered}

To determine which SDG each MSP addressed, a dictionary-based quantitative text analysis was employed. The dictionary (see annex 2) is based on the '[Global indicator framework for the Sustainable Development Goals and targets of the 2030 Agenda for Sustainable Development](https://unstats.un.org/sdgs/indicators/Global%20Indicator%20Framework%20after%202020%20review_Eng.pdf)' and was developed, tested, and revised by team-members at IVM and SU and contained `r dictionary %>% nrow()` unigrams, bigrams and trigrams, i.e. combinations of 1, 2 or 3 words. Each SDG was assigned to a number of keywords of concepts. Three corpora were created with unigrams, bigrams and trigrams, each consisting of some nearly 3 million observations. The corpora were subsequently matched with the dictionary in a document-term matrix (DTM) consisting of some 23.000 observations.

```{r, echo=FALSE}

head(tt_dtm_all_t2030)
```

*Example of document-term matrix*

### Operationalization and coding {.unnumbered}

To determine whether the entry could be considered an MSP we operationalized Liliana Andonova's (2017) definition of MSPs, "voluntary agreements between public and non-state actors on a set of governance objectives and norms, rules, practices, implementation procedures, across multiple jurisdictions and levels of governance", through the following four criteria. 

Table 1. Operationalization of MSP definition

| **Criterion \#** | **Requirements**                                                                                                                                                                                                    |
|-------------|-----------------------------------------------------------|
| 1                | Does the entry involve partners from more than one of the following sectors: public, private, civil society?                                                                                                        |
| 2                | Are the partners based in more than one jurisdiction?                                                                                                                                                               |
| 3                | Are the partners targeting more than one jurisdiction?                                                                                                                                                              |
| 4                | Does the entry display elements of institutionalization (e.g. governance objectives and norms, rules, practices, implementation procedures)? If yes, what level of institutionalization does the entry demonstrate? |

Based on this operationalization, each of the 2452 observations were manually coded to determine which entries fulfill all criteria of the definition and can thus be considered to be an MSP. The first three criteria are coded as dummy variables, to identify whether or not there are minimum two partners in the initiative that come from different sectors, are based in more than one jurisdiction and target more than one jurisdiction through their cooperation. The fourth criterion is a categorical variable that captures the extent to which observations describe "a set of governance objectives and norms, rules, practices, implementation procedures" (Andonova 2017). It differentiates between two tiers of entries indicating whether they adhere to a strict or loose definition of MSPs. The operationalization is provided in Table 2, and was determined from the entries' own descriptions about their organizational set-up and activities. We consider the focus of this project to lie within the entries that fulfilled the first three criteria and are in Tier 1 and 2 \`r  nrow(MSPs)\`. 

Table 2. Operationalization of the categorical variable on whether entries adhere to a strict or loose definition of MSPs. 

| **Tier** | **Operationalization**                                                                                                                                                                                                                     | **Example from the Transform 2030 data-set**                                                                                                                                                                                                                                                |
|-------------|--------------------------|---------------------------------|
| 1        | Entries that display a governance structure with rules, decision-making bodies and formal procedures (e.g. collective action networks)                                                                                                     | Global Alliance for Buildings and Construction (GlobalABC): A global alliance of stakeholders that aims to transform the buildings and construction industry through five work areas and subsequent processes and projects, implemented by partners, steering committees and a secretariat. |
| 2        | Entries that display short-term, temporary or more loosely organized initiatives. Or entries that describe a part of/a product of a larger governance structure and goal (e.g. a project in a programme of an international organization). | iDiaspora: A project with the main output being a global engagement and knowledge exchange hub. It is open to partnering with stakeholders to disseminate their knowledge, but does not display substantial decision-making procedures etc.                                                 |
| 3        | Other types of activities (e.g. corporate sustainability strategies, sales products, country commitments)                                                                                                                                  | Mobile Advisory Services LTD: A company's strategy on how to align its activities with the goals of government ministries.                                                                                                                                                                  |

Furthermore, in order to identify whether the MSPs are active or no longer perform their work, their level of activity was assessed by scanning their homepages and other relevant websites to identify their most recent activity. The main reasons for recording their activity are to identify which MSPs that are or have been in function, that thereby may be generating or may have generated effects through their work and could be researched further. In specific, their level of activity was coded according to the following categories:

Table 3. Operationalization of the categorical variable of activity level

| **Activity level** | **Operationalization**                                                                     |
|----------------|--------------------------------------------------------|
| Active             | Evidence of activity since 1st January 2019                                                |
| Concluded          | Evidence of concluded activities, or last activity was before 1st January 2019             |
| Inactive           | Launch described on UN DESA platform or elsewhere but no additional information available. |

Lastly, additional variable coding was carried out for all the observations that qualified for the data-set. While our scraping exercise captured basic information about the partnership, such as the geographies they are connected to and the types of resources they self-report, the additional variable coding was carried out manually to translate self-reported information into a more reliable and uniform format with more easily comparable values. The latter capture information about the partnerships' the number and type of stakeholders that participate in the partnerships and the functions of the partnership. In total, as a result of the scraping and the manual data collection, the Transform 2030 data-set consists of 48 variables (see Transform 2030 data-set code-book for further information).

### Caveats and remedies {.unnumbered}

The methodology is subject to a set of limitations. First, the dictionary approach is sensitive to omitted keywords and sentences, potentially reducing the reliability of choosing MSPs addressing two or more SDGs. Being aware of this, the dictionary was carefully crafted and extensively discussed by researchers at Stockholm University and IVM through a series of iterations to identify ambiguous wordings. For instance, words such as "women", "management" and "resources'' were removed from earlier versions of the dictionary since they were difficult to attribute to one single SDG.

Another challenge is the intercoder reliability when coding the criteria of our MSP operationalization. To increase reliability, the coding team performed two rounds of reliability tests on random samples of entries. The commonalities and discrepancies were subsequently discussed and existing guidelines in the codebook were adjusted. During the coding process, the team also frequently consulted each other to ensure highest possible coherence. Furthermore, the observations in the data-set underwent a second round of revision, since the variable coding was often conducted by a different coder than the coder for the MSP criteria. Nevertheless, despite the team's effort to identify and mitigate methodological risks wherever possible, there may be cases and coding where human errors could still be found. All such cases are completely the responsibility of the report writers and can be communicated to the authors.

Further, it is important to note that although this is probably the most complete source of partnerships for sustainable development, we cannot claim this to be representative data of the whole universe of transnational MSPs. It is hard to determine whether there is a language barrier that makes it difficult for some MSPs to register, or even be aware of platforms like this one. We noted some well known and established MSPs to not be registered in this platform. The reasons why stakeholders may or may not register is out of the scope of our research, but some potential explanations could be that they fail to perceive any added value from registering, they don't have the administrative capacity to do so and manage possible extra tasks that may come with it, or the platform itself has not been given enough visibility for MSPs to even be aware of it.

A final caveat worth pointing out is that most of the data coded for every observation is based on their provided description on the UN DESA Partnership Platform. Given that the registration form on the platform has been updated on several occasions, the descriptions were not equal in format, with variations in the amount and type of information provided. Efforts were taken to double-check unclear instances by briefly visiting their websites, however in general it applies that the coded data is based on the descriptions.

## Annex 2 - Dictionary {.unnumbered}

```{r, echo=FALSE}
dictionary %>% 
  select(SDG,word) %>% 
  mutate(SDG = as.character(SDG)) %>% 
  print(n=Inf)
```

## Annex 3 - Active and Concluded Multi-stakeholder partnerships in T2030 database

```{r, echo=FALSE}

rbind(MSPs_tier1, MSPs_tier2) %>% # This variable is created in one of the figures
  select(name, Tier) %>% 
  dplyr::rename("Name of multi-stakeholder partnership in database" = name) %>% print(n=Inf)
```
